### 2024-04-30 Paper/paper.tex
Updates from Overleaf

    Before presenting the main results of the paper, I investigate whether executive team changes are occurring endogenously due to the programs. If hospitals change their propensity to hire a clinically trained executive because they expect to be penalized or want to avoid penalties, then there is selection in the independent variable. First, I analyze whether changes in clinically trained executives are concentrated around the program enactment, 2011-2012. Second, I analyze whether hospitals who end up getting penalized are more likely to change clinically trained executives on their team than non-penalized hospitals. That is, are hospitals that expect to be more affected by the initial penalties more likely to hire or fire clinically trained executives? I consider changes along having any clinically trained executive as well as changes in the number of clinically trained executives. I estimate the following regression equations:

@@

@@

>>>>

    Before presenting the main findings, I investigate whether executive team changes occur endogenously due to the programs. If hospitals change their propensity to hire a clinically trained executive because they expect to be penalized or want to gain extra payments, then there is selection in the independent variable. First, I analyze whether changes in clinically trained executives are concentrated around the enactment of both HRRP and HVBP, 2011-2012. Second, I analyze whether hospitals who end up getting penalized through HRRP are more likely to change clinically trained executives on their team than non-penalized hospitals, and similarly for hospitals who end up getting extra payments for high quality of care through HVBP. That is, are hospitals that expect to be more affected by the programs more likely to hire or fire clinically trained executives? I consider changes along having any clinically trained executive as well as changes in the number of clinically trained executives. I estimate the following regression equations:

@@

    \import{Tables}{MD_noMD_readmort_decomp_synth.tex}

@@

    \import{Tables}{MD_noMD_uncompCMI_decomp_synth.tex}

### 2024-04-30 Tables/MD_noMD_readmort_decomp_synth.tex
Updates from Overleaf

\caption{\label{tab:MD_noMD_readmort_decomp_synth}Decomposition of Readmissions and Mortality for Nonprofits Synthetic DiD Results}
\centering
\begin{tabular}[t]{lcccl}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{2}{c}{Weighted Avg. Readmission Rate} & \multicolumn{2}{c}{Weighted Avg. Mortality Rate} \\
\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5}
 & (1) & (2) & (1) & (2)\\
\midrule
Ever MD Executive x Post 2012 & 0 &  & -0.06 & \\
 & (0.07) &  & (0.06) & \\
2012 MD Executive x Post 2012 &  & -0.19$^{*}$ &  & -0.1\\
 &  & (0.09) &  & (0.09)\\
 &  &  &  \vphantom{1} & \\
\addlinespace
\textbf{Comparison Group:} &  &  &  & \\
Never MD & $\checkmark$ &  & $\checkmark$ & \\
Has MD not in 2012 &  & $\checkmark$ &  & $\checkmark$\\
 &  &  &  & \\
Observations & 3925 & 1845 & 3910 & 1840\\
\bottomrule
\end{tabular}
\end{table}

>>>>

\caption{\label{tab:MD_noMD_readmort_decomp_synth}Decomposition of Readmissions and Mortality for Nonprofits Synthetic DiD Results}
\centering
\begin{tabular}[t]{lcccl}
\toprule
\multicolumn{1}{c}{ } & \multicolumn{2}{c}{Weighted Avg. Readmission Rate} & \multicolumn{2}{c}{Weighted Avg. Mortality Rate} \\
\cmidrule(l{3pt}r{3pt}){2-3} \cmidrule(l{3pt}r{3pt}){4-5}
 & (1) & (2) & (1) & (2)\\
\midrule
Ever MD Executive x Post 2012 & 0 &  & -0.06 & \\
 & (0.07) &  & (0.06) & \\
2012 MD Executive x Post 2012 &  & -0.19$^{*}$ &  & -0.1\\
 &  & (0.09) &  & (0.09)\\
 &  &  & & \\
\addlinespace
\textbf{Comparison Group:} &  &  &  & \\
Never MD & $\checkmark$ &  & $\checkmark$ & \\
Has MD not in 2012 &  & $\checkmark$ &  & $\checkmark$\\
 &  &  &  & \\
Observations & 3925 & 1845 & 3910 & 1840\\
\bottomrule
\end{tabular}
\end{table}
